Adversarial State Aggregation

### 2019-11-06 minutia/paper/paper.tex
paper troubleshooting and references

@@

    Reassuring achievements in the Deep RL in a variety of fields absorb the attention from the community
    \citep{Mnih2015, Schulman2015TrustOptimization, Lillicrap2015ContinuousDDPG, silver2016a}. The cross
    fertilization in using approximation techniques by Deep Neural Networks in solving immense state space problems
    in RL is a key. While the newly emerged methods are growing at a staggering pace, a parallel area of research
    has been formed wherein a variety of techniques have been utilized to make these methods contravene their
    promised functionality. These efforts would be served to develop robustness in those spectacular models and
    reduce their susceptibility to data tampering or dynamics of the environment. Robustness ---as a property in
    machine learning--- elevates assurance about methods performance and their reliability to the foreground. In a
    few studies \cite{Goodfellow2014}  vulnerabilities of DNN's to adversarially-manipulated inputs are revealed.
    Therefore, robust algorithms, have to be of paramount importance in applying deep RL to real world scenarios to
    mitigate risks of implementation. Adversarial attacks as a way to perturbing these algorithms, are introduced in
    recent works \cite{Huang2017, Kos2017} from different aspects to degrade algorithms' performance. One of such
    potentials are changes in the environment dynamics.

@@

    The main goal of adversarial training and examples can be expressed briefly in form of the following equation:
    \begin{equation}
        \begin{aligned}
            & \underset{\theta}{\min}
            & & \sum_{x,y \in S} \underset{\delta \in \Delta}{\max}
            & & & \textbb{Loss}(x + \delta, y; \theta)
        \end{aligned}
    \end{equation}

@@

    Let $s_\eta$ be the perturbed observation and $s_c$ scaled observation, so we are trying to find the following:
    \begin{equation}
        \begin{aligned}
            & \underset{s}{\argmin}
            & & {\norm{s_\eta - s_c}} = \norm{s . (1 + \eps) - s_c}
        \end{aligned}
    \end{equation}
    which is the state observation that have the minimum distance between real-world [scaled] observation and the perturbed one.

@@

    \section{Adversarial attacks on different methodologies}
    Here we review adversarial attacks on a variety of value function based state-of-art algorithms proposed by the community so far. As \cite{Pattanaik2018} pointed out, the concept of achieving a successful adversarial attack is unalike in reinforcement learning tasks compared to image classification tasks. Worst \textit{action} is tangible and feasible but not worst \textit{image}.

    \subsection{Deep Q Learning (DQN)}
    Utilizing experience replay and the leveraging target network, DQN take advantage of them to gain more stability \cite{Pattanaik2018}.

    \section{Experiment}
    We apply the approach to two MDPs proposed by \cite{Strehl2004AnProcesses}. \textit{RiverSwim} an MDP consists of six states and \textit{SixArms} one with seven states. In \textit{RiverSwim} flow of the river is to left and the swimmer picks probabilistically equal either state 1 or 2 as the start point. All states but two terminal states have zero reward to land at while the right most one rewards substantially higher than the other one. The agent in SixArms selects between six distinct actions which pulls different arms of a multi-armed bandit. By pulling an arm the agent traverses to a new state. Although the agent does not obtain reward by pulling the arms but going to the connected state to that arm is highly rewarding in which the transition probability is in inverse relationship with the reward value.

    As both problems favor keeping the agent in states with lower reward, exploration is paramount to maximize the accumulated reward. This is also confirmed by the authors in \cite{Strehl2004AnProcesses} that the agent will fail to learn when a rudimentary $\epsilon$-greedy algorithm.

    Our implementation uses Deep Q-Network (DQN) \cite{Mnih2015} as the policy optimizer. OpenAI Gym \cite{BrockmanOpenAIGym} is the testbed in the benchmarks in this paper. In training phase, models are trained in the environment. Online methods such as DQN learn by interacting directly in the environment, however, CRAAM

>>>>

% SHi-ON packages
% argmin argmax begin
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
% argmin argmax end
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}        % norm using amsmath

@@

    Reassuring achievements in the Deep RL in a variety of fields absorb the attention from the community
    \citep{Mnih2015, schulman2015a, Lillicrap2015, silver2016a}. The cross
    fertilization in using approximation techniques by Deep Neural Networks in solving immense state space problems
    in RL is a key. While the newly emerged methods are growing at a staggering pace, a parallel area of research
    has been formed wherein a variety of techniques have been utilized to make these methods contravene their
    promised functionality. These efforts would be served to develop robustness in those spectacular models and
    reduce their susceptibility to data tampering or dynamics of the environment. Robustness ---as a property in
    machine learning--- elevates assurance about methods performance and their reliability to the foreground. In a
    few studies \cite{Goodfellow2014}  vulnerabilities of DNN's to adversarially-manipulated inputs are revealed.
    Therefore, robust algorithms, have to be of paramount importance in applying deep RL to real world scenarios to
    mitigate risks of implementation. Adversarial attacks as a way to perturbing these algorithms, are introduced in
    recent works \cite{Huang2017, Kos2017} from different aspects to degrade algorithms' performance. One of such
    potentials are changes in the environment dynamics.

@@

    The main goal of adversarial training and examples can be expressed briefly in form of the following equation:
    %    \begin{equation}
    %        \begin{aligned}
    %            & \underset{\theta}{\min}
    %            & & \sum_{x,y \in S} \underset{\delta \in \Delta}{\max}
    %            & & & \textbb{Loss}(x + \delta, y; \theta)
    %        \end{aligned}
    %    \end{equation}

@@

    Let $s_\eta$ be the perturbed observation and $s_c$ scaled observation, so we are trying to find the following:
    \begin{equation}
        \begin{aligned}
            & \underset{s}{\argmin}
            & & {\norm{s_\eta - s_c}} = \norm{s . (1 + \epsilon) - s_c}
        \end{aligned}
    \end{equation}
    which is the state observation that have the minimum distance between real-world [scaled] observation and the perturbed one.

@@

    \section{Experiment}
    We apply the approach to two MDPs proposed by\cite{Strehl2004}. \textit{RiverSwim} an MDP consists of six states and \textit{SixArms} one with seven states. In \textit{RiverSwim} flow of the river is to left and the swimmer picks probabilistically equal either state 1 or 2 as the start point. All states but two terminal states have zero reward to land at while the right most one rewards substantially higher than the other one. The agent in SixArms selects between six distinct actions which pulls different arms of a multi-armed bandit. By pulling an arm the agent traverses to a new state. Although the agent does not obtain reward by pulling the arms but going to the connected state to that arm is highly rewarding in which the transition probability is in inverse relationship with the reward value.

    As both problems favor keeping the agent in states with lower reward, exploration is paramount to maximize the accumulated reward. This is also confirmed by the authors in \cite{Strehl2004} that the agent will fail to learn when a rudimentary $\epsilon$-greedy algorithm.

    Our implementation uses Deep Q-Network (DQN)\cite{Mnih2015} as the policy optimizer. OpenAI Gym \cite{Brockman2016} is the testbed in the benchmarks in this paper. In training phase, models are trained in the environment. Online methods such as DQN learn by interacting directly in the environment, however, CRAAM
